Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

\medskip
Viscous flow instabilities can be found across several disciplines and scales, from chemical separation processes to geological reservoir fluids. \citet{muskat_1934} investigated the flow of a fluid injected between two infinite parallel plates (Hele-Shaw cell) and the impact on capillary number ($N_{c}$),
\begin{equation}
N_{c} = \frac{\mu U}{\gamma},
\label{eq:capillary_number}
\end{equation}
where $\mu$ is the viscosity of the fuid, $\gamma$ is the surface tension and $U$ is a velocity characteristic of the moving interface.

\medskip
In Hele-Shaw cells, a fluid is introduced between two parallel flat plates separated by an infinitesimally small gap. The experimental apparatus allows the predicted instability to be verified qualitatively and simplifies the problem of flow in both porous and non-porous media.   
%The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law) since the Hele-Shaw apparatus may be used for both porous and non-porous media.  
More recently, \citet{howison_2000} and \citet{praud_2005} gave a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells (also know as Saffman $\&$ Taylor problem). For a Hele-Shaw cell of a given size the developing flow only depends on the capillary number. Thus if \textit{$N_{c}$} is too high \citet{saffman_1959}, \citet{homsy_1987} and \citet{tabeling_1987} agreed that the flow develops into a single steady-state finger which moves through the cell with constant velocity $U$.

>>>>

\medskip
Viscous flow instabilities can be found across several disciplines and scales, from chemical separation processes to geological reservoir fluids. \citet{muskat_1934} investigated the flow of a fluid injected between two infinite parallel plates (Hele-Shaw cell) and the impact on capillary number ($N_{c}$),
\begin{equation}
N_{c} = \frac{\mu U}{\gamma}.
\label{eq:capillary_number}
\end{equation}
In Eqn.~\ref{eq:capillary_number}, $\gamma$ is the surface tension and $U$ is the characteristic velocity of the moving interface. In Hele-Shaw cells, a fluid is introduced between two parallel flat plates separated by an infinitesimally small gap. This experimental apparatus enables instabilities to be qualitatively investogated by simplifying the flow problem in both porous and non-porous media.   
%The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law) since the Hele-Shaw apparatus may be used for both porous and non-porous media.  
More recently, \citet{howison_2000} and \citet{praud_2005} gave a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells (also know as Saffman $\&$ Taylor problem). For a Hele-Shaw cell of a given size the developing flow only depends on the capillary number. Thus if \textit{$N_{c}$} is too high \citet{saffman_1959}, \citet{homsy_1987} and \citet{tabeling_1987} agreed that the flow develops into a single steady-state finger which moves through the cell with constant velocity $U$.
